Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Paris version \YellowPaperVersionNumber}}

### 2023-12-15 Paper.tex
wording, and remove extra line in equation

\hypertarget{block_header_validity_function}{}Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv & H_{\mathrm{g}} \le H_{\mathrm{l}}  \quad \wedge \\
\nonumber& & H_{\mathrm{l}} < {P(H)_{\mathrm{H}}}_{\mathrm{l}'} + \left\lfloor\frac{{P(H)_{\mathrm{H}}}_{\mathrm{l}'}}{1024}\right\rfloor  \quad \wedge \\
\nonumber& & H_{\mathrm{l}} > {P(H)_{\mathrm{H}}}_{\mathrm{l}'} - \left\lfloor\frac{{P(H)_{\mathrm{H}}}_{\mathrm{l}'}}{1024}\right\rfloor  \quad \wedge \\
\nonumber& & H_{\mathrm{l}} \geqslant 5000  \quad \wedge \\
\nonumber& & H_{\mathrm{s}} > {P(H)_{\mathrm{H}}}_{\mathrm{s}} \quad \wedge \\
\nonumber& & H_{\mathrm{i}} = {P(H)_{\mathrm{H}}}_{\mathrm{i}} +1 \quad \wedge \\
\nonumber& & \lVert H_{\mathrm{x}} \rVert \le 32 \quad \wedge \\
\nonumber& & H_{\mathrm{f}} = F(H) \wedge \\
\nonumber& & H_{\mathrm{o}} = \mathtt{KEC}( \mathtt{RLP}([]) ) \quad \wedge \\
\nonumber& & H_{\mathrm{d}} = 0 \quad \wedge \\
\nonumber& & H_{\mathrm{n}} = \texttt{0x0000000000000000} \quad \wedge \\
\nonumber& & H_{\mathrm{a}} = \mathtt{PREVRANDAO}() \\
\end{eqnarray}

@@

Unlike all previous hard forks of Ethereum, \textit{Paris} was not defined to occur at a particular block height, but rather at a \textit{terminal total difficulty}.
Total difficulty was used to avoid a scenario in which a minority of hash power could create a malicious fork that could race to satisfy the block height requirement and claim the first proof of stake block.

>>>>

\hypertarget{block_header_validity_function}{}Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv & H_{\mathrm{g}} \le H_{\mathrm{l}}  \quad \wedge \\
\nonumber& & H_{\mathrm{l}} < {P(H)_{\mathrm{H}}}_{\mathrm{l}'} + \left\lfloor\frac{{P(H)_{\mathrm{H}}}_{\mathrm{l}'}}{1024}\right\rfloor  \quad \wedge \\
\nonumber& & H_{\mathrm{l}} > {P(H)_{\mathrm{H}}}_{\mathrm{l}'} - \left\lfloor\frac{{P(H)_{\mathrm{H}}}_{\mathrm{l}'}}{1024}\right\rfloor  \quad \wedge \\
\nonumber& & H_{\mathrm{l}} \geqslant 5000  \quad \wedge \\
\nonumber& & H_{\mathrm{s}} > {P(H)_{\mathrm{H}}}_{\mathrm{s}} \quad \wedge \\
\nonumber& & H_{\mathrm{i}} = {P(H)_{\mathrm{H}}}_{\mathrm{i}} +1 \quad \wedge \\
\nonumber& & \lVert H_{\mathrm{x}} \rVert \le 32 \quad \wedge \\
\nonumber& & H_{\mathrm{f}} = F(H) \wedge \\
\nonumber& & H_{\mathrm{o}} = \mathtt{KEC}( \mathtt{RLP}([]) ) \quad \wedge \\
\nonumber& & H_{\mathrm{d}} = 0 \quad \wedge \\
\nonumber& & H_{\mathrm{n}} = \texttt{0x0000000000000000} \quad \wedge \\
\nonumber& & H_{\mathrm{a}} = \mathtt{PREVRANDAO}()
\end{eqnarray}

@@

Unlike all previous hard forks of Ethereum, \textit{Paris} was not defined to occur at a particular block height, but rather after a specified \textit{terminal total difficulty} was reached.
Total difficulty was used instead of block height to avoid a scenario in which a minority of hash power could create a malicious fork that could race to satisfy the block height requirement and claim the first proof of stake block.
